Language-Based Security for Low-Level MPC

### 2024-05-13 ppdp24/model.tex
checkpoint

We consider random tapes to be selected from a uniform distribution
modulo relevant pre-processing, e.g., Beaver triples for efficient
multiplication, and/or MACed share distributions as in SPDZ \cite{XXX}.
We will also assume that any possible initial secrets
are equally likely when formulating the program distribution.
We define $\runs(\prog)$ as the set of final memories resulting
from execution of $\prog$ given any initial memory, and
treat all elements of $\runs(\prog)$ as equally likely.
This establishes the basic program distribution that can be
marginalized and conditioned to quantify input/output
information dependencies. 
%In this
%setting, given a program $\prog$ with $\iov(\prog) = S \cup V$ and
%$\flips(\prog) = F$ we will consider all $\store \in \mems(S \cup V
%\cup F)$ such that $ \config{\store_{S \cup F}}{\prog} \redxs
%\config{\store_}{\varnothing} $ to be equally probable, establishing
%the basic distribution of the program. %From this, we can immediately
%derive the marginal distribution of $S \cup V$ to reason about
%dependencies between secrets and views.
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given $\prog$ with $\secrets(\prog) = S$ and $\flips(\prog) = R$ and
  pre-processing predicate $\preproc$ on memories, define:
  $$
  \runs(\prog) \defeq \{ \store \mid \preproc(\store) \wedge
  %(\dom(\store) = \iov(\prog) \cup R) \wedge
  (\store_{S \cup R},\prog) \redxs (\store,\varnothing) \}
  $$
  Then the \emph{basic distribution of $\prog$}, written $\progtt(\prog)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\store) =  1 / |\runs(\prog)| \ \text{if}\ \store \in \runs(\prog), \text{otherwise}\ 0
  $$
  In some cases, we will also be concerned with the (joint)
  probabilities of expression interpretation given a preceding program
  execution, and we write $\progtt(\prog, \be)$ to denote the program
  distribution $\progtt(\prog;\itv := \be)$ where $\itv$ is a
  special variable that is never used in programs.
\end{definition}

@@

It is necessary to add $\bot$ to the range of memories since
the possibility of abort needs to be reflected in adversrarial
runs of a protocol. We can define $\aruns(\prog,\adversary)$
as the ``prefix'' memories that result from possibly-aborting
protocols, but we also need to ``pad out'' the memories
of partial runs with $\bot$, as we defin in $\botruns(\prog,\adversary)$,
to properly reflect the contents of views and outputs even in case of abort. 
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given program $\prog$ with $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$, and
  any assumed pre-processing predicate $\preproc$ on memories, define:
  $$
    \aruns(\prog) \defeq 
    \{ \store \mid \preproc(\store)  \wedge ((\store_{S\cup R},\prog) \aredx^* (\store,\varnothing)\}% \vee (\store_{S \cup R},\prog) \aredx^* (\store,\bot)) \}
  $$
  and also define the following which pads out undefined views and outputs with $\bot$:
  $$
  \begin{array}{l}
    \botruns(\prog) \defeq \\
    \qquad \{ \store\{ x_1 \mapsto \bot, \ldots, x_n \mapsto \bot \} \mid \\
    \qquad \phantom{\{} \store \in \aruns(\prog) \wedge \{ x_1,\ldots,x_n\} = (V \cup O) - \dom(\store) \}
  \end{array}
  $$
  Then the \emph{$\adversary$ distribution of $\prog$}, written $\progtt(\prog,\adversary)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\prog,\adversary) =  1 / |\botruns(\prog)| \ \text{if}\ \store \in \botruns(\prog), \text{otherwise}\ 0
  $$
\end{definition}

>>>>

We consider random tapes to be selected from a uniform distribution
modulo relevant pre-processing, e.g., Beaver triples for efficient
multiplication, and/or MACed share distributions as in SPDZ \cite{XXX}.
We will also assume that any possible initial secrets
are equally likely when formulating the program distribution.
We define $\runs(\prog)$ as the set of final memories resulting
from execution of $\prog$ given any initial memory, and
treat all elements of $\runs(\prog)$ as equally likely.
This establishes the basic program distribution that can be
marginalized and conditioned to quantify input/output
information dependencies. 
%In this
%setting, given a program $\prog$ with $\iov(\prog) = S \cup V$ and
%$\flips(\prog) = F$ we will consider all $\store \in \mems(S \cup V
%\cup F)$ such that $ \config{\store_{S \cup F}}{\prog} \redxs
%\config{\store_}{\varnothing} $ to be equally probable, establishing
%the basic distribution of the program. %From this, we can immediately
%derive the marginal distribution of $S \cup V$ to reason about
%dependencies between secrets and views.
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given $\prog$ with $\secrets(\prog) = S$ and $\flips(\prog) = R$ and
  pre-processing predicate $\preproc$ on memories, define:
  $$
  \begin{array}{c}
    \runs(\prog) \defeq \\
    \{ \store \mid \exists \store_1 \in \mems(R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \cap \store_2,\prog) \redxs (\store,\varnothing) \}
  \end{array}
  $$
  Then the \emph{basic distribution of $\prog$}, written $\progtt(\prog)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\store) =  1 / |\runs(\prog)| \ \text{if}\ \store \in \runs(\prog), \text{otherwise}\ 0
  $$
  By default, $\preproc(\store) \iff \dom(\store) = S$, i.e.,
  the initial memory contains all input secrets in a uniform
  marginal distribution.

  In some cases, we will also be concerned with the (joint)
  probabilities of expression interpretation given a preceding program
  execution, and we write $\progtt(\prog, \be)$ to denote the program
  distribution $\progtt(\prog;\itv := \be)$ where $\itv$ is a
  special variable that is never used in programs.
\end{definition}

@@

It is necessary to add $\bot$ to the range of memories since
the possibility of abort needs to be reflected in adversrarial
runs of a protocol. We can define $\aruns(\prog,\adversary)$
as the ``prefix'' memories that result from possibly-aborting
protocols, but we also need to ``pad out'' the memories
of partial runs with $\bot$, as we defin in $\botruns(\prog,\adversary)$,
to properly reflect the contents of views and outputs even in case of abort. 
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given program $\prog$ with $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$, and
  any assumed pre-processing predicate $\preproc$ on memories, define:
  $$
  \begin{array}{c}
    \aruns(\prog) \defeq \\
    \{ \store \mid \exists \store_1 \in \mems(R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \cap \store_2,\prog) \aredxs (\store,\varnothing) \}
  \end{array}
  $$
  and also define the following which pads out undefined views and outputs with $\bot$:
  $$
  \begin{array}{l}
    \botruns(\prog) \defeq \\
    \qquad \{ \store\{ x_1 \mapsto \bot, \ldots, x_n \mapsto \bot \} \mid \\
    \qquad \phantom{\{} \store \in \aruns(\prog) \wedge \{ x_1,\ldots,x_n\} = (V \cup O) - \dom(\store) \}
  \end{array}
  $$
  Then the \emph{$\adversary$ distribution of $\prog$}, written $\progtt(\prog,\adversary)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\prog,\adversary) =  1 / |\botruns(\prog)| \ \text{if}\ \store \in \botruns(\prog), \text{otherwise}\ 0
  $$
\end{definition}
